Curriculum and Imitation Learning for Bipedal Locomotion on Rough Terrain

### 2019-02-02 paper/rss/main.tex
edits to section II

Many approaches to locomotion on physical robots use optimization-based planning with detailed models.
These approaches tend to generate \emph{hierarchical} plans in order to reduce computational requirements.
First, they choose footstep locations using search, like A* \citep{huang2013step}.
Based on the footstep plan, they generate a CoM trajectory with a simplified physics model such as a spring-loaded inverted pendulum \citep{mordatch2010robust} or contact wrench cone \citep{dai2016planning}.
Then they use inverse kinematics to plan trajectories for end-effectors \citep{zucker2010optimization}.
Finally, these trajectories are optimized using the full dynamics model to account for obstacles and other details \citep{ratliff2009chomp}.

>>>>

Many approaches to locomotion on physical robots use optimization-based planning with detailed models.
These approaches tend to generate \emph{hierarchical} plans in order to reduce computational requirements.
At the highest level, the planner chooses footstep locations using, e.g. A* search~\citep{huang2013step}.
Based on the footstep plan, a lower-level planner generates a CoM trajectory with a simplified physics model such as a spring-loaded inverted pendulum~\citep{mordatch2010robust} or contact wrench cone~\citep{dai2016planning}.
Next, inverse kinematics are used to plan trajectories for end-effectors \citep{zucker2010optimization}.
Finally, these trajectories are optimized using the full dynamics model to account for obstacles and other details~\citep{ratliff2009chomp}.
